An Embedding Framework for Consistent Polyhedral Surrogates

### 2020-03-05 journal/poly-embed.tex
Adding images and fixing paths
Adding a new example from hierarchical paper.

\begin{figure}
\begin{center}
\begin{minipage}{0.32\linewidth}
\includegraphics[width=\linewidth]{./tikz/abstain-link-linf.pdf}
\end{minipage}\hfill
\begin{minipage}{0.32\linewidth}
\includegraphics[width=\linewidth]{./tikz/abstain-link-U-regions-l1.pdf}
\end{minipage}\hfill
\begin{minipage}{0.32\linewidth}
\includegraphics[width=\linewidth]{./tikz/abstain-link-l1.pdf}
\end{minipage}\hfill
\caption{Constructing links for the abstain surrogate $L_{1/2}$ with $d=2$. The embedding is shown in bold labeled by the corresponding reports. (L) The link envelope $\Psi$ resulting from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.  (M) An illustration of the thickened sets from Definition~\ref{def:eps-thick-link} for two sets $U \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$. (R) The $\Psi$ and $\psi$ from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_1$ and $\epsilon = 1$.}
\label{fig:abstain-links}
\end{center}
\end{figure}

@@

>>>>

\begin{figure}
\begin{center}
\begin{minipage}{0.32\linewidth}
\includegraphics[width=\linewidth]{tikz/abstain-link-linf.pdf}
\end{minipage}\hfill
\begin{minipage}{0.32\linewidth}
\includegraphics[width=\linewidth]{tikz/abstain-link-U-regions-l1.pdf}
\end{minipage}\hfill
\begin{minipage}{0.32\linewidth}
\includegraphics[width=\linewidth]{tikz/abstain-link-l1.pdf}
\end{minipage}\hfill
\caption{Constructing links for the abstain surrogate $L_{1/2}$ with $d=2$. The embedding is shown in bold labeled by the corresponding reports. (L) The link envelope $\Psi$ resulting from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.  (M) An illustration of the thickened sets from Definition~\ref{def:eps-thick-link} for two sets $U \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$. (R) The $\Psi$ and $\psi$ from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_1$ and $\epsilon = 1$.}
\label{fig:abstain-links}
\end{center}
\end{figure}

@@

\proposedadd{New example using hierarchical surrogate}
\subsection{Embedding hierarchical classifications}
Our final example comes from Ramaswamy et al.~\cite{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
\begin{equation}\label{eq:tree-loss-discrete}
	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
\end{equation}
In this setting, the outcomes $\Y$ are composed of all nodes in the tree and not just the leaves.

\jessie{TODO: Add in example Tikz tree from tikz/hierarchical-property.tex}
\begin{figure}
	\centering
		\includegraphics[width=0.8\linewidth]{tikz/example-tree-deeper.pdf}
		\caption{Tree with distribution $\vec p = (0, .2, .1, .4, .3)$. $gamma(\vec p) = 3$.}
\end{figure}

\begin{figure}
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree.pdf}
	\caption{3 node tree whose property we evaluate in next image.}
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree-prop.pdf}
	\caption{Property elicited by unweighted 3-node tree.}
\end{minipage}
\end{figure}

In~\cite[Theorem 1]{ramaswamy2015hierarchical}, they show the property $\gamma := \prop{\ell^H}$ is the deepest node $i$ in the tree $H$ such that the probability that node $i$ or one of its descendants is the outcome is greater than or equal to $1/2$.

In this model, consider $p_i$ to be the probability that node $i$ is the ground truth label, and $S_i(p)$ to be the probability that node $i$ or one of its descendants is the ground truth.

Letting $h$ be the height of the tree $H$, Ramaswamy et al. present an embedding of $\ell^H$ that consists of learning $h$ $\abstain{1/2}$ embeddings, where the outcomes at the $j^{th}$ embedding are the nodes on level $j$ of the tree.
At each highest level, one proceeds down the path of the tree given by the prediction of the current abstain embedding.
If one predicts $\bot$ at level $j$, then we predict the node predicted at the $(j-1)^{st}$ level.

Note that the given \emph{Cascade Surrogate} of~\cite[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\cite{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.
